Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
x

\begin{figure}[tb]
\centering
\begin{tabular}{lrl}
\toprule
\textbf{Protocol} & \textbf{LoC} & \textbf{Challenging features} \\ 
\midrule
DNS packets & 48+64 & Label compression,\\
  & & count fields \\
ZIP archives & 92+78 & Checksums, offsets, \\ 
  & & variable length trailer, \\
  & & compression \\
Ethernet & 16 & --- \\
ARP & 10 & --- \\
IP & 25 & Total length field, options \\
UDP & 7 & Checksum, length field \\
ICMP & 5 & Checksum \\
\bottomrule
\end{tabular}

>>>>

\begin{figure}[tb]
\centering
\begin{tabular}{lrl}
\toprule
\textbf{Protocol} & \textbf{LoC} & \textbf{Challenging features} \\ 
\midrule
DNS packets & 48+64 & Label compression,\\
  & & count fields \\
ZIP archives & 92+78 & Checksums, offsets, \\ 
  & & variable length trailer, \\
  & & compression \\
Ethernet  & 16+0\phantom{0} & --- \\
ARP       & 10+0\phantom{0} & --- \\
IP        & 25+0\phantom{0} & Total length field, options \\
UDP       &  7+0\phantom{0} & Checksum, length field \\
ICMP      &  5+0\phantom{0} & Checksum \\
\bottomrule
\end{tabular}
